\documentclass{exam}
%\printanswers
\begin{document}

\section{Decisions and MDPs}

\begin{questions}

\question Suppose you are a turtle guru, and you have found your way into a turtle-themed spinoff of "Who Wants To Be A Millionaire". You have gotten to the 50,000 turtle question, and would win 15,500 turtles if you decide to quit before seeing the 50,000 turtle question. You have a 14 percent chance of getting the next question right. What is the expected payoff of going for the next question? What is the optimal decision?
\begin{solution}
\end{solution}

\question Is a sequence of actions sufficient to get an agent in a nondeterministic environment to reach some goal?
\begin{solution}
\end{solution}

\question What are the components of an MDP?
\begin{solution}
\end{solution}

\question In class, we talked about an example environment where taking the "North" action was nondeterministic. Is it possible for all actions in an environment to be nondeterministic? 
\begin{solution}
\end{solution}

\question \textbf{(No Answer Necessary)} Review any gopollock questions you got wrong at ter.ps/cmsc389fgp3
\begin{solution}
\end{solution}

\end{questions}

\section{Exploring OpenAI and GridWorld}

Note: This week, we will begin a very cursory exploration of OpenAI Gym and FrozenLake (a version of the GridWorld environment that we discussed in class). We will solve FrozenLake in later lectures and assignments using a variety of RL algorithms that we will learn. \\

\begin{questions}

\question
\textbf{OpenAI's FrozenLake}
\begin{itemize}
\item Open the view-only Python 3 Notebook at ter.ps/cmsc389fhw3
\item Click on "File", "Save a Copy in Drive"
\item Go to your copy of the notebook and complete the exercises
\item Share your finished notebook with cmsc389f@gmail.com, "HW2 - First Name, Last Name"
\end{itemize}

\end{questions}

% \ifprintanswers
% You're currently in LaTeX solution mode!
% \else
% NOTE: If you'd like to answer in LaTeX, uncomment \textbackslash printanswers at the top!
% \fi

\end{document}

